Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-10-01 paper.tex
Updated Paper
Work in progress.

    One contribution of this paper is to proof that it is possible to
    evolve a population of individuals, similar to a Genetic Algorithm (GA),
    using a distributed, parallel, and asynchronous methodology by algorithm
    implementation and testing.

>>>>

    One contribution of this paper is to prove that it is possible to
    evolve a population of individuals, similar to a Genetic Algorithm (GA),
    using a distributed, parallel, and asynchronous methodology by algorithm
    implementation and testing.
